Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-09 papers/SiVL2018/sivl_2018.tex
defines new commands
intermediate commit

\title{Do we need object naming beyond entry-level categories?} % Replace with your title

@@

While traditional approaches to computer vision have often focussed on categorizing and classifying visual content according to predefined annotation schemes (for e.g.\ object categories, attributes or actions), research on language \& vision typically aims at predicting or generating natural verbal descriptions of visual objects and scenes depicted in images or videos.
In recent years, there has been an explosion of interest in language \& vision tasks in the NLP community, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,chen2015mind,vinyals:show,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016,schlazar:acl16}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
All of these tasks require models that capture linguistic and visual knowledge at the same time, i.e. determining which combinations of words are appropriate for a given visual scene and, potentially, in a given discourse context, cf.\ \cite{vries2017guesswhat}.
Moroever, in contrast to rigid classification often used in computer vision, the target output in language \& vision is usually more flexible and varies in terms of a range of factors:  different speakers might have different preferences when describing an object, and the same speaker might prefer different descriptions depending on the task or context.
%next to knowledge about visual categories, require , thecomplex verbal utterances need to be produced, and in some cases, these utterances not only need to describe visual content, but also need to be appropriate in a relatively complex .

@@

%But even though almost every task in language \& vision involves the prediction of object names (e.g. image captioning, referring expression generation, visual dialogue), hardly any research has explicitly looked at object naming, i.e.\ determining the actual word or concept that speakers would use to refer to an object (in a particular context), but see \cite{Ordonez:2016,zarriess-schlangen:2017}.
Even research in pragmatics, that traditionally deals with reference and referring expression production, has mostly focused on attributes, rather than object names.
Recently, however, \cite{graf2016animal} have shown that object naming preferences \textit{are} subject to pragmatic factors: in a typical reference game set-up with images of target objects, each  presented along with images of distractor objects, speakers have been found to flexibly adjust object names depending on the context. For instance, a \textit{dalmatian} would be called \textit{dalmatian} in the context of other dogs or simply \textit{dog} when none of the distractors is also a dog.
This extends previous traditional work on concepts suggesting that the typicality of a referent determines its entry-level category (and consequently, its name) \cite{Rosch1978}.

>>>>

\title{Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora} % Replace with your title

@@

Understanding and modeling the way humans converse about their environment using natural language has been a long-standing goal of research in various fields related to artificial intelligence and linguistics.
But, for a long time, computational research into language grounding, reference and situated interaction had to rely on ``block-worlds'' or very controlled, experimental environments \cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref}, leading to models and corresponding findings at a rather restricted scale.
This situation has radically changed with recent developments in the language \& vision community. 
Pushed especially by developments in computer vision, there has been an explosion of interest in language \& vision tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,chen2015mind,vinyals:show,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016,schlazar:acl16}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.

Despite this dramatic progress in the field, however, a lot of research in language \& vision still centers around systems for very specific tasks and data sets.

@@

%But even though almost every task in language \& vision involves the prediction of object names (e.g. image captioning, referring expression generation, visual dialogue), hardly any research has explicitly looked at object naming, i.e.\ determining the actual word or concept that speakers would use to refer to an object (in a particular context), but see \cite{Ordonez:2016,zarriess-schlangen:2017}.
%Even research in pragmatics, that traditionally deals with reference and referring expression production, has mostly focused on attributes, rather than object names.
%Recently, however, \cite{graf2016animal} have shown that object naming preferences \textit{are} subject to pragmatic factors: in a typical reference game set-up with images of target objects, each  presented along with images of distractor objects, speakers have been found to flexibly adjust object names depending on the context. For instance, a \textit{dalmatian} would be called \textit{dalmatian} in the context of other dogs or simply \textit{dog} when none of the distractors is also a dog.
%This extends previous traditional work on concepts suggesting that the typicality of a referent determines its entry-level category (and consequently, its name) \cite{Rosch1978}.
